---
title: "Confidence and Prediction Intervals"
subtitle: "What are and when to use them"
author: "Kael Huerta"
date: "August, 2016"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'),
  echo = F, message = F, warning = F)
options(htmltools.dir.version = FALSE)
```

```{r}
## Libraries
library(data.table)
library(tidyr)
library(ggplot2)
library(plyr)
library(dplyr)
theme_set(theme_bw())
```



```{r}
## Generated dataset
set.seed(3003)
dates <- seq(as.Date('2016-01-01'), as.Date(Sys.time()), by = 'day')
n <- length(dates)
trend <- cumsum(sample(c(-.5, .5), n, replace = T, prob = c(3/8, 5/8)))
seas <- c(5, 1, 0, 3, 6, 8, 7)
noise <- cumsum(rnorm(n, 0, 1))
data <- data.table(dates, Trend = trend, `Weekly Seasonality` = seas,
    `White Noise` = noise) %>%
  mutate(Sales = Trend + `Weekly Seasonality` + `White Noise`)
```








# tl;dr

The *confidence intervals* are recommended for checking where the adjusted
model lies.
The *prediction intervals* are recommended for checking where the
predicted values may lie.

### Tags

```
#confidence, #prediction, #probability #intervals
```

# Confidence and Prediction Intervals


Let us start with an example to ilustrate the differences between the
intervals.

Suppose we run a business that recently has been increasing its sales and we
do not get a lot of clients during weekends. 
il



```{r, echo = F, fig.cap = 'Notice how the trend is going upwards and we have little dips each weekend'}
data %>%
  gather(variable, value, -dates) %>%
  ggplot(aes(x = dates, y = value, colour = variable)) +
    # geom_point() +
    geom_line() +
    facet_wrap(~variable, ncol = 1, scale = 'free_y') +
    xlab('Date') + ylab('') +
    theme(legend.position = 'none')
```



```{r fig-margin, fig.margin = TRUE, fig.cap = "MPG vs horsepower, colored by transmission.", fig.width=3.5, fig.height=3.5, cache=TRUE}
library(ggplot2)
mtcars2 <- mtcars
mtcars2$am <- factor(
  mtcars$am, labels = c('automatic', 'manual')
)
ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point() + geom_smooth() +
  theme(legend.position = 'bottom')
```
